\LARGE \bf Artificial Cognition for Social Human-Robot Interaction:\\ An Implementation

### 2016-06-30 paper.tex
Update on Overleaf.

Aligning the upper part of the ontology on {\sc OpenCyc} (as done by other
knowledge representation systems, like {\sc KnowRob}~\cite{Tenorth2009a} or PEIS
K\&R~\cite{daoutis2012cooperative}) has multiple advantages. First the design of
this part of the ontology is generally difficult: it pertains to abstract
concepts whose mutual relations comes to philosophical debates. The upper
taxonomy of {\sc OpenCyc} represents a relative consensus, at least within the
semantic Web community. Then, because it is a well established project with
numerous links to other on-line databases (like Wikipedia or WordNet), the reuse
of key {\sc OpenCyc} concepts ensures that the knowledge stored by the robot can
be shared or extended with well-defined semantics. The concept of \emph{Object}
represents a typical case of ambiguous meaning: in everyday conversation, an
object is a relatively small physical thing, that can be typically manipulated.
A human is not usually considered as an object. {\sc OpenCyc} however precisely
defines an object as anything at least \emph{partially tangible}. This includes
obviously the humans, and actually many other entities that would not be
commonly said to be objects (the Earth for instance).\footnote{In such cases of
discrepancy between {\sc OpenCyc} concepts and human terminology, we manually
label the {\sc OpenCyc} concepts with appropriate human names: for instance, the
OpenRobots Ontology associates the label ``\emph{object}'' to the concept
\concept{cyc:Artifact} instead of the concept \concept{cyc:PartiallyTangible}.
These labels are used in priority during the grounding of verbal interactions.}
Thus the importance of relying on well-defined and standard semantics to
exchange information between artificial systems in a non-ambiguous way.

@@

The integration of these components in a consistent, working and observable
system builds upon the particular design of the interfaces between the cognitive
components: the information streams use high-level semantics, represented as
first-order logic statements. In that sense, our deliberative architecture is
similar to projects like {\sc cram}~\cite{Beetz2010}, KeJia~\cite{Chen2010} or
PEIS Ecology~\cite{saffiotti2005peis, daoutis2012cooperative}, with however a
stronger emphasize on the representation and interaction with humans. We however
distinguish ourselves from research on \emph{cognitive architectures}: cognitive
architectures are usually understood as an artificial yet principled model of
(human) cognition. While some have been deployed on autonomous robots, like
HAMMER~\cite{demiris2006hierarchical} or ACT-R/E~\cite{trafton2013act}, most are
primarily concerned with the modeling of human cognition and are less focused on
practical deployment on socially interactive robots.

>>>>

Aligning the upper part of the ontology on {\sc OpenCyc} (as done by other
knowledge representation systems, like {\sc KnowRob}~\cite{Tenorth2009a} or PEIS
K\&R~\cite{Daoutis2009}) has multiple advantages. First the design of this part
of the ontology is generally difficult: it pertains to abstract concepts whose
mutual relations comes to philosophical debates. The upper taxonomy of {\sc
OpenCyc} represents a relative consensus, at least within the semantic Web
community. Then, because it is a well established project with numerous links to
other on-line databases (like Wikipedia or WordNet), the reuse of key {\sc
OpenCyc} concepts ensures that the knowledge stored by the robot can be shared
or extended with well-defined semantics. The concept of \emph{Object} represents
a typical case of ambiguous meaning: in everyday conversation, an object is a
relatively small physical thing, that can be typically manipulated. A human is
not usually considered as an object. {\sc OpenCyc} however precisely defines an
object as anything at least \emph{partially tangible}. This includes obviously
the humans, and actually many other entities that would not be commonly said to
be objects (the Earth for instance).\footnote{In such cases of discrepancy
between {\sc OpenCyc} concepts and human terminology, we manually label the {\sc
OpenCyc} concepts with appropriate human names: for instance, the OpenRobots
Ontology associates the label ``\emph{object}'' to the concept
\concept{cyc:Artifact} instead of the concept \concept{cyc:PartiallyTangible}.
These labels are used in priority during the grounding of verbal interactions.}
Thus the importance of relying on well-defined and standard semantics to
exchange information between artificial systems in a non-ambiguous way.

@@

The integration of these components in a consistent, working and observable
system builds upon the particular design of the interfaces between the
cognitive components: the information streams use high-level semantics,
represented as first-order logic statements. In that sense, our deliberative
architecture is similar to projects like {\sc cram}~\cite{Beetz2010} or PEIS
Ecology~\cite{saffiotti2005peis, daoutis2012cooperative}, with however a
stronger emphasize on the representation and interaction with humans. We
however distinguish ourselves from research on \emph{cognitive architectures}:
cognitive architectures are usually understood as an artificial yet principled
model of (human) cognition. While some have been deployed on autonomous robots,
like HAMMER~\cite{demiris2006hierarchical} or ACT-R/E~\cite{trafton2013act},
most are primarily concerned with the modeling of human cognition and are less
focused on practical deployment on socially interactive robots.
